Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-06-27 num_result.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

We start with the process
\begin{equation}
\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
\end{equation}
and show its Loschmidt echo in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast. The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.02n \pi$, $n = 1,...,25 $. The fitting is performed before the finite size revival surges and error is estimated by assuming iid Gaussian distribution of the each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

@@

Next we analyze the more interesting $\theta$ dependent process
\begin{equation}
  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

@@

Finally, we also provide the data for the process
\begin{equation}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, in a way that is not captured by our analytic calculation. Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$. 
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of Loschmidt echo in the process ${\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P}$. The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$. }
\label{fig:PDN_fit}
\end{figure}

>>>>

We start with the process
\begin{equation}
\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
\end{equation}
and show its Loschmidt echo in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast. The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $. The fitting is performed before the finite size revival surges and error is estimated by assuming iid Gaussian distribution for each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

@@

Next we analyze the more interesting $\theta$ dependent process
\begin{equation}
  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: The exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

@@

Finally, we also provide the data for the process
\begin{equation}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation. Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$. 
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of Loschmidt echo in the process ${\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P}$. The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$. }
\label{fig:PDN_fit}
\end{figure}
